### 2019-10-01 uiuc.tex
airports and typos

\subsubsection{Accessibility and Accomodation}
 A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy. Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year. CU-MTD charges an affordable rate of \$1 per ride, which can be paid in cash or using the Token Transit app. Additionally, an all-day pass can be bought on Saturdays and Sundays for \$2 from any bus operator or from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and rideshare services are also plentiful. There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports. Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.

\subsubsection{Weather}
With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather and spring coming into bloom. Holding a conference during this time would be the perfect way to showcase our beautiful city.

>>>>

\subsubsection{Accessibility and Accomodation}
 Many hotels are located around downtown Champaign and the Eastern 
 side of campus, making transportation easy. Champaign-Urbana Mass Transit 
 (CU-MTD) is a reliable public transportation service that sees millions of 
 riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
 can be paid in cash or using the Token Transit app. Additionally, an all-day 
 pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
 from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
 rideshare services are also plentiful.
 Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
Charlotte (CLT). Finally, Peoria Charter is a popular bus service with several 
daily trips between the UIUC campus and the Chicagoland area.

\subsubsection{Weather}
With an average high temperature of 65$^{\circ}$ and an average low temperature 
of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter 
weather and spring coming into bloom. Holding a conference during this time 
will be the perfect way to showcase our beautiful city.
